Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-10 AKSZ.tex
dbro comments
changes

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\p\!\!\!\p}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}
%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\section{The AKSZ formalism and para-geometry}
\def\fg{\mathfrak{g}}
In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
The construction closely follows the relationship between ordinary (non-para) generalized complex structures and $2D$ topological field theories developed by Gualtieri, Pestun, \brian{other references?}.

The prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}., but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.

Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
\brian{cite Severa} \cite{SeveraTduality}.

In Section \ref{??}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}.

All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism. 
Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry which is the essential ingredient in this construction.

@@

\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
First, we recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
For a reference, see \cite{Roytenberg:2002nu,??}.

From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
\brian{give citations here.}

\brian{recollection on shifted symplectic NQ manifolds}

In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.

@@

We briefly recount the construction of the $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.

@@

Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \to E \to T$, the latter is the anchor and the first map is the linear dual to the anchor.
Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
The body of the NQ manifold is $M$, and the underlying graded vector bundle is given by $T^*[2] \oplus E[1]$. 
Define the degree $+1$ vector field 
\[
Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
\]
as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
\[
(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
\]
define
\begin{align*}
(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
\end{align*}

All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
In local coordinates \brian{finish}

@@

The starting point of the AKSZ construction is the mapping space
\begin{equation}\label{eqn: map}
\cE (M, X) = {\rm Map}\left((M, (\sA^*_M, \d_M)), X\right)
\end{equation}
where 
\begin{itemize}
\item $(M, (\sA^*_M, \d_M))$ is an {\em $n$-oriented} dg manifold with body a smooth oriented manifold $M$. \brian{recall $n$-orientation.}
\item $X$ is a $(n-1)$-shifted symplectic NQ manifold. 
\end{itemize}

The dg manifold $(M, \sA^*_M)$ is specified by a sheaf of graded commutative algebras $\sA^*_M$ over the de Rham complex $\Omega^*_M$.
Here, $\d_M$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
\begin{itemize}
\item[(1)] $\sA_M$ is concentrated in finitely many degrees;
\item[(2)] For each $k$, $\sA^k_M$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
\item[(3)] The differential $\d_M : \sA_M^* \to \sA_M^{*+1}$ is square zero differential operator making $(\sA_M , \d_M)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_M$
\end{itemize}

In particular, as a graded algebra $\sA^*_M$ is given by functions on a graded manifold $A_M$ with body $M$.
In other words, $A_M$ is the total space of some graded vector bundle on $M$ (which is of finite rank and concentrated in finitely many degrees). 
As a graded manifold, the mapping space $\cE(M,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_M$ and $X$.

\begin{Ex}
The most important example for us will be the source dg manifold $(M, \Omega^*_M)$, that is $\sA_M = \Omega^*_M$ equipped with de Rham differential. 
We denote this dg manifold by $M_{\rm dR}$.
Take the dg manifold $(M, \Omega^*_M)$ where $M$ is any smooth manifold. 
If $M$ is closed and oriented there exists an integration map
\[
\int_M : \Omega^*_M \to \RR[n]
\]
of degree $-n$ thus equipping the dg manifold $M_{\rm dR}$ with an $n$-orientation. 
\end{Ex}

\begin{Ex}
If $M$ has a para-complex structure, $(M, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
We will denote this dg manifold by $M_{\pd}$. 
To equip the dg manifold $(M, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
One way to do this is to assume that the para-complex manifold $M$ is equipped with a para-holomorphic volume form $\Omega_X$. \brian{is this defined earlier?}
\end{Ex}

In this case, that $\dim(M) = n$ and $X = (X, \omega_X)$ is an $(n-1)$-shifted symplectic NQ manifold, then the AKSZ construction endows the mapping space $\cE(M, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form. 
The fundamental observation is that the diagram
\[
\xymatrix{
& M \times \cE(M, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_M} & \\
M & & X
}
\]
induces a pairing
\[
\begin{array}{ccccc}
 \Omega^p_M & \times & \Omega^q_N & \to & \Omega^{p+q-n}_{\cE(M, X)} \\
\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_M \pi_M^* \alpha \wedge {\rm ev}^* \beta 
 \end{array}
 \]
Applied to the element $1 \times \omega_X \in \Omega^0_M \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_M \omega_X$.

@@

From here on, to any Courant algebroid $E$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.

@@

\begin{Ex} \label{ex: exact CA}
The action functional is
\[
S = \int_M p_i \d x^i + \frac{1}{2} g_{ab} e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} c(x)_{abc} e^{a} e^b e^c .
\]
\end{Ex}
\subsubsection{Dirac structures and boundary conditions}

@@

Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.

In general, when $M$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(M)$ will with $(-1)$-shifted symplectic structure. 
However, the space $\cE(\partial M)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(M)$. 
Morever, the natural restriction map $\cE(M) \to \cE(\partial M)$ is a Lagrangian morphism in the sense of \cite{PTVV}.

@@

A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial M)$.
The intersection $\cL \times_{\cE(M)} \cE(\partial M)$ of the two Lagrangians $\cL$ and $\cE(\partial M)$

@@

\begin{Ex}
Suppose $(X, \pi)$ is a Poisson manifold. 
Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
\[
{\rm Graph}(\pi) = \{(\pi \vee \alpha , \alpha) \; | \; \alpha \in T^* \} \subset \TT .
\]
By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $M^3$ with $\partial M = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model. \brian{reference}
\end{Ex}

@@

\brian{Recall that a generalized (para-)complex structure $\JJ$ defines a Dirac structure in $\TT$, and hence a Lagrangian inside of the $2$-shifted symplectic space $\XX_H$.  
%More generally, if $\JJ$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $\XX_E$. 
This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory. }

By this general construction, we see that any GpC structure $\KK$ defines a 2D TFT as a boundary theory to the 3D theory whose target is the standard Dorfman Courant algebroid.

Recall that Theorem \ref{thm:pairofdirac} tells us that the choice of a GpC structure $\KK$ determines a pair of tansversal Dirac structures $L$ and $\tilde{L}$. 
Moreover, by Proposition \ref{prop:dirac_Liealg} the eigenbundle $L$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.

@@

\subsubsection*{Trivial GpC structure}

@@

Another special case of a generalized para-complex structure is para-complex structure.

@@

@@

@@

 \brian{discuss anomalies}

@@

\end{document}

\section{The AKSZ formalism and 3d TFT}
\def\fg{\mathfrak{g}}
In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}. 
The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.

Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
For a reference, see \cite{Roytenberg:2002nu,??}.

\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
\brian{give citations here.}

In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid.

We briefly recall this construction.

>>>>

\documentclass{article}
\usepackage{amssymb, amsmath, amsthm, mathtools, bbm, tikz-cd,stmaryrd,enumerate,hyperref}
%-------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
%----------------
\newcommand{\TT}{{T\oplus T^*}}
\newcommand{\JJ}{\mathcal{J}}
\newcommand{\KK}{\mathcal{K}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\Cc}{\mathbf{C}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\XX}{\mathfrak{X}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\FF}{\mathcal{F}}
\newcommand{\QQ}{\mathcal{Q}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cN}{\mathcal{N}}
%----------------------------------------
\newcommand{\PP}{\mathrm{P}}
\newcommand{\PPt}{\tilde{\mathrm{P}}}
\newcommand{\id}{\mathbbm{1}}
\newcommand{\nlr}{\overset{\leftrightarrow}{\n}}
\newcommand{\lc}{\mathring{\n}}
\newcommand{\im}{\mathrm{Im}\,}
\newcommand{\Ker}{\mathrm{Ker}\,}
\newcommand{\Lie}{\mathcal{L}}
\newcommand{\PS}{\mathcal{P}}
\newcommand{\ap}{\alpha}
\newcommand{\bt}{\beta}
\def\w{\wedge}
\newcommand{\p}{\partial}
\newcommand{\pt}{\tilde{\partial}}
\newcommand{\xt}{{\tilde{x}}}
\newcommand{\n}{\nabla}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\PH}{(\PS,\eta,\omega)}
\newcommand{\Lt}{\tl{L}}
\newcommand{\Lb}{\mathbb{L}}
\newcommand{\s}{\mathbf{s}}
\newcommand{\se}{\Gamma}
\newcommand{\Endo}{\text{End}}
\newcommand{\ellt}{{\tl{\ell}}}
\newcommand{\ot}{{1/2}}
\newcommand{\inv}{{-1}}
\newcommand{\Aa}{\mathcal{A}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\lara}{\la\ ,\ \ra}
\newcommand{\brac}{[\ ,\ ]}
\newcommand{\bl}{[\![}
\newcommand{\br}{]\!]}
\newcommand{\bracd}{\bl \ ,\ \br}
\newcommand{\yt}{\tl{y}}
\newcommand{\zt}{\tl{z}}
\newcommand{\tth}{\tl{\theta}}
\newcommand{\kk}{\mathrm{k}}
\newcommand{\Mt}{\tl{M}}
\newcommand{\pd}{\overline{\p\!\!\!\p}}
\newcommand{\Mb}{\mathbb{M}}
\newcommand{\Drm}{\mathrm{D}}
\newcommand{\Dcal}{\mathcal{D}}
\newcommand{\wtl}{\widetilde}

%----------------------------------------
\def\gld{generalized Lie derivative }
\def\glds{generalized Lie derivatives }
\def\tl{\tilde}

@@

\section{The AKSZ formalism and para-geometry}
\def\fg{\mathfrak{g}}
In this section we will show how to associate a class of $2D$ topological field theories to generalized para-complex structures.
The construction closely follows the relationship between ordinary (non-para) generalized complex structures \cite{Gualtieri:2003dx} and $2D$ topological field theories developed in \cite{Cattaneo:2009zx, Pestun:2006rj} \btd{Please add any more references you think fit.}

The prescription of defining the $2D$ topological theory associated to a GpC structure starts with a $3D$ topological field theory which is defined for any manifold $M$. 
More generally, this $3D$ theory can be defined for any {\em Courant algebroid} on $M$ \cite{Roytenberg:2002nu}, but for most examples we will only consider the standard exact Courant algebroid (or twisted versions) defined by the Dorfman bracket.
The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$.

Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of the $3D$ topological theory defined by the standard Courant algebroid.
For another class of $2D$ boundary theories to the $3D$ Courant algebroid $\sigma$-model see \cite{SeveraTduality}.

In Section \ref{sec: twist}, we will relate these theories topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} closely following the methods in \cite{Kapustin:2004gv} for ordinary generalized complex geometry.

All of the topological field theories in this section are of $\sigma$-model type and arise through the AKSZ formalism \cite{AKSZ}. 
Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry which is the essential ingredient in this construction.

@@

\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}

From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
We recall the construction of the $3D$ topological field theory from the data of a Courant algebroid. 
For other references, see \cite{Roytenberg:2002nu, Cattaneo:2009zx}.

\subsubsection{Shifted symplectic geometry} 
\label{sec: dgman}

We begin by setting up our model for the theory of derived manifolds. 
This is a well-behaved class of $NQ$ manifolds which are appropriate for setting up quantization of $\sigma$-models, see for instance \cite{CostelloSUSY}. 
A dg manifold is a pair $\cN = (N, \sA^*_N)$ where $N$ is a smooth manifold, called the body, and $\sA^*_N$ a sheaf of graded commutative algebras over the de Rham complex $\Omega^*_N$.
Here, $\d_N$ is a linear differential operator of degree $+1$, and together the data must satisfy the following conditions:
\begin{itemize}
\item[(1)] $\sA_N$ is concentrated in finitely many degrees;
\item[(2)] For each $k$, $\sA^k_N$ is a locally free sheaf of $C^\infty_M$-modules of finite rank;
\item[(3)] The differential $\d_N : \sA_N^* \to \sA_N^{*+1}$ is square zero differential operator making $(\sA_N , \d_N)$ into a sheaf of commutative dg algebras over the de Rham complex $\Omega^*_N$.
\end{itemize}

In particular, as a graded algebra $\sA^*_N$ is given by functions on a graded manifold $A_N$ with body $N$.
In other words, $A_N$ is the total space of some graded vector bundle on $N$ (which is of finite rank and concentrated in finitely many degrees). 
In the language of $NQ$ manifolds, the homological vector field $Q$ is $\d_N$.

In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic dg manifold from the data of a Courant algebroid.

@@

We briefly recount the equivalence between the data of a $2$-shifted symplectic NQ manifold $X_E$ and the data of a Courant algebroid $E$.

@@

%Given any Courant algebroid $E \to M$, we can have the following sequence of maps $T^* \xto{a^*} E \xto{a} T$ where $a$ is the anchor and $a^*$ is linear dual to the anchor.
%Using this sequence, we can define the associated $NQ$ manifold $X_E$, following \cite{Ryotenberg:2002nu}.
Let $E \to M$ be a vector bundle equipped with a fiberwise nondegenerate inner product $\left<-,-\right>$.
The body of the NQ manifold is the manifold $M$, and the underlying graded manifold $X_E$ is given by $T^*[2] \oplus E[1]$.

We will use coordinates $\{x^i\}$ on $M$, $\{p_i\}$ for the fiber coordinate of $T^*$, and $\{e^a\}$ for the fiber of $E$. 
Note that $x^i$ is of degree zero, $\eta_i$ is of degree $2$, and $e^a$ is of degree $1$.
Suppose also that $\left<e^a, e^b\right> = g^{ab}$ and let $(g_{ab})$ be the inverse to the inner product. 
Notice, $X_E$ comes equipped with a natural $2$-shifted symplectic form, which in coordinates is 
\[
\omega_E = d x^i d p_i + g_{ab} d e^a d e^b .
\]
Denote by $\{-,-\}$ the shifted Poisson bracket corresponding to this symplectic structure. 
An arbitrary degree $3$ function on the graded manifold $X_E$ has the form
\[
\Theta = p_i a_a^i (x) e^a + \frac{1}{6} f_{abc} (x) e^a e^b e^c .
\]
Globally, $a = (a_a^i)$ defines a bundle map $a : E \to T$ and through the pairing the collection $(f_{abc})$ defines a bilinear map $[-,-] : E \times E \to E$. 
It is a result of \cite{Roytenberg:2002nu} that this function satisfies $\{\Theta, \Theta\} = 0$ if and only if the data $(E, \left<-,-\right>, a, [-,-])$ has the structure of a Courant algebroid. 
Here $a$ is the anchor map, and $[-,-]$ is the bracket.

%\[
%Q : \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) \to \Gamma(M , \Sym \left(T^*[2] \oplus E[1]\right)^*) 
%\]
%as follows: for $\psi \in \Sym^{k + \ell + 2} \left(T^*[2] \oplus E[1]\right)^*)$ and
%\[
%(\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell) \in \Sym^{k+1}(T^*[2]) \otimes \Sym^{\ell + 1}(E[1]) 
%\]
%define
%\begin{align*}
%(Q \psi) ((\xi_0 \otimes \cdots \otimes \xi_k) \otimes (\alpha_0 \otimes \cdots \otimes \alpha_\ell)) = \brian{finish}
%\end{align*}
%
%All that remains is to describe the $2$-shifted symplectic structure on the NQ manifold $X_E$. 
%This is defined via the obvious pairing between $T^*[2]$ and $T$ together with the pairing $\langle - ,- \rangle$ on $E[1]$.
%In local coordinates \brian{finish}

@@

Fix the following data:
\begin{itemize}
\item an {\em $n$-oriented} dg manifold $\cN = (N, (\sA^*_N, \d_\cN))$ with body a smooth oriented manifold $N$ and orientation $\mu$. 
\item An $(n-1)$-shifted symplectic dg manifold $(X,\omega)$. 
\end{itemize}

The starting point of the AKSZ construction is the mapping space
\begin{equation}\label{eqn: map}
\cE (\cN, X) = {\rm Map}\left(\cN, X\right)
\end{equation}
As a graded manifold, the mapping space $\cE(N,X)$ is given by the space of smooth maps between the underlying graded manifolds $A_N$ and $X$. 
The graded manifold $\cE(\cN, X)$ is equipped with the homological vector field $\d_\cN + Q$ where $Q$ is the homological vector field on $X$.

The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
The fundamental observation is that the diagram
\[
\xymatrix{
& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
N & & X
}
\]
induces a pairing
\[
\begin{array}{ccccc}
 \Omega^p_N& \times & \Omega^q_X & \to & \Omega^{p+q-n}_{\cE(N, X)} \\
\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
 \end{array}
 \]
Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{\brian{??}}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.

\begin{Ex}
The most important example for us will be the source dg manifold $(N, \Omega^*_N)$, that is $\sA_N = \Omega^*_N$ equipped with de Rham differential. 
We denote this dg manifold by $N_{\rm dR}$.
Take the dg manifold $(N, \Omega^*_N)$ where $N$ is any smooth manifold. 
If $N$ is closed and oriented there exists an integration map
\[
\int_N : \Omega^*_N \to \RR[n]
\]
of degree $-n$ thus equipping the dg manifold $N_{\rm dR}$ with an $n$-orientation. 
\end{Ex}

\begin{Ex}
If $N$ has a para-complex structure, $(N, \mathbf{\Omega}^{0,\bullet})$ has the structure of a dg manifold. 
Here $\mathbf{\Omega}^{0,\bullet}$ is the para-Dolbeault complex from Section \ref{sec: paracomplex} with differential given by the para $\pd$-operator. 
We will denote this dg manifold by $N_{\pd}$. 
To equip the dg manifold $(N, \mathbf{\Omega}^{0,\bullet})$ with an orientation, one must fix additional data. 
One way to do this is to assume that the para-complex manifold $N$ is equipped with a para-holomorphic volume form $\Omega_N$. \brian{Cite David's new section.}
\end{Ex}

@@

From here on, to any Courant algebroid $E$ on a manifold $M$ we associate the NQ manifold $X_E$ which carries a $2$-shifted symplectic structure. 
In the case that the Courant algebroid is exact, call the associated $2$-shifted symplectic space $X_H$, where $H$ labels the Severa class.

@@

\begin{Ex} \label{ex: exact CA}
If $E$ is a Courant algebroid on $M$ let $X_E$ be the corresponding $2$-shifted symplectic manifold.
We use the same coordinates as in Section \ref{sec: dgman}.
The action functional is
\[
S = \int_N p_i \d x^i + \frac{1}{2} g_{ab}(x) e^a \d e^b - a_a^i(x) p_i e^a + \frac{1}{6} f_{abc} (x) e^{a} e^b e^c .
\]
\end{Ex}

@@

Suppose $N$ is a manifold with boundary, and let $\cE(N)$ denote the space of fields of a classical theory on $M$. 
For us, $\cE(N)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
Let $\cE(\partial N)$ denote the restriction of the fields to the boundary of $N$. 
For the mapping space example, this is simply the space of maps ${\rm Map}(\partial N, X)$.

In general, when $N$ is not closed, the pairing defined by the AKSZ construction will not endow $\cE(N)$ will with $(-1)$-shifted symplectic structure. 
However, the space $\cE(\partial N)$ does carry a natural ordinary ($0$-shifted) symplectic structure from the restriction of the pairing defined on $\cE(N)$. 
Morever, the natural restriction map $\cE(N) \to \cE(\partial N)$ is a Lagrangian morphism in the sense of \cite{PTVV}.

@@

A boundary condition is the choice of an additional Lagrangian subspace $\cL$ of $\cE(\partial N)$.
The intersection $\cL \times_{\cE(N)} \cE(\partial N)$ of the two Lagrangians $\cL$ and $\cE(\partial N)$

@@

\begin{Ex}
Suppose $(M, \pi)$ is a Poisson manifold. 
Then consider the graph of $\pi$ as a Lagrangian subbundle of $\TT$:
\[
{\rm Graph}(\pi) = \{(\pi \vee \alpha , \alpha) \; | \; \alpha \in T^* \} \subset \TT .
\]
By the Jacobi identity, this subbundle is integrable and so determines a Dirac structure. 
If we place the 3D AKSZ theory with target the Courant algebroid $\TT$ on $N^3$ with $\partial N = \Sigma$, the boundary condition determined by this Dirac structure is equivalent to the Poisson $\sigma$-model on $\Sigma$, see \cite{KSSdirac}, for instance.
\end{Ex}

@@

Let $M$ be a manifold.
Throughout this section we will only consider the standard Dorfman Courant algebroid $X_H$ on $M$, possibly twisted by an $H$-flux.
By Theorem \ref{thm:pairofdirac}, the choice of a GpC structure $\KK$ determines a pair of transversal Dirac structures $L$ and $\tilde{L}$ on $M$ given by the positive and negative eigenbundles of $\KK$. 
In particular, $L$ determines a Lagrangian in the shifted symplectic space $X_{H}$. 
This Lagrangian then defines a boundary condition for the three-dimensional AKSZ theory.
Thus, we see that any GpC structure $\KK$ defines a 2D TFT living at the boundary of the 3D theory.

\begin{remark}
More generally, if $\KK$ is a generalized complex structure in an arbitrary Courant algebroid $E$, then we obtain a $2$-shifted Lagrangian inside of the $2$-shifted symplectic space $X_E$. 
\end{remark}

Moreover, by Proposition \ref{prop:dirac_Liealg} the eigenbundle $L$ has the structure of a Lie algebroid compatible with the anchor and Dorfman bracket on $\TT$.

@@

\subsubsection*{Trivial GpC structures}

Let $M$ be a smooth manifold.
Consider the case of the trivial generalized para-complex structure on $M$ defined by
\begin{align*}
\KK_0=
\begin{pmatrix}
\id & 0 \\
0 & -\id
\end{pmatrix}.
\end{align*}
The positive eigenbundle is simply $L = T$.

\brian{Trivial Poisson $\sigma$-model, AKA $BF$ theory.}

@@

Another special case of a generalized para-complex structure is para-complex structure.
In this case, the generalized AKSZ theory specializes to the following para-complex version of the $B$-model.

@@

The classical BRST cohomology of the para-B-model is isomorphic to the cohomology of para-holomorphic polyvector fields on the target para-complex manifold $X$.
To see the equivalence of this definition with the generalized description of the AKSZ model, note that the Lie algebroid $L$ \brian{finish}

\brian{discuss anomalies. Para-holomorphic volume form.}

@@

\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}

@@

@@

\bibliographystyle{alpha}
\bibliography{mybib}
\end{document}

%\section{The AKSZ formalism and 3d TFT}
%\def\fg{\mathfrak{g}}
%In this section we will show how to associate $2D$ topological theories to a generalized (para-)complex structure and relate them to the topological twists of $2D$ $(2,2)$ (para-)SUSY sigma models described in Section \ref{sec:toptwist} and in \cite{Kapustin:2004gv}. 
%The key to our construction is to realize the data of a G(p)C structure in terms of its eigenbundles, which are Dirac structures $L$ in the Courant algebroid $\TT$. 
%Via the AKSZ construction \cite{AKSZ}, this correspondence translates into the statement that the Dirac structure $L$ defines a topological boundary theory of a $3D$ topological theory defined by the Courant algebroid $\TT$ \cite{Roytenberg:2002nu}.
%
%Throughout, we will use symplectic $NQ$ manifold as our model for shifted symplectic geometry. 
%We will recall the general setup of associating a $3D$ topological field theory to the data of a Courant algebroid. 
%For a reference, see \cite{Roytenberg:2002nu,??}.
%
%\subsection{Courant algebroids, $3D$ TFTs, and boundary conditions}
%From the point of view of topological field theory, Courant algebroids are important because they provide geometric examples of $2$-shifted symplectic spaces. 
%Via the AKSZ construction, $2$-shifted symplectic spaces are the natural home for $3$-dimensional topological field theories in the BV formalism. 
%\brian{give citations here.}
%
%In \cite{Roytenberg:2002nu}, it is shown how to associate a $2$-shifted symplectic NQ manifold from the data of a Courant algebroid. 
%
%\begin{theorem}[\cite{Roytenberg:2002nu}]
%There is an equivalence between isomorphism classes of $2$-shifted symplectic NQ manifolds with body $M$ and isomorphism classes of Courant algebroids on $M$.
%\end{theorem}
%
%We briefly recall this construction. 
%
%Recall, the data of a Courant algebroid on a manifold $M$ is a vector bundle $E$, whose sheaf of sections we denote $\cE$, together with a nondegenerate symmetric bilinear pairing $\langle -, -\rangle : \cE \otimes \cE \to C^\infty(M)$ , an anchor map $a : E \to T M$, and a bilinear operator
%\[
